A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-25 03_Prep_data.Rmd
Revert "revert"
This reverts commit 30490337c4f7b9c9bb7bdccc0a51f93beb21c7a1.
Fix heading levels and report the median disease pressure

### Disease pressure factor

@@

median_AUDPC <-
   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)

@@

### Row spacing

We may want to consider row spacing in the trials.
However one of the locations has `NA` as the row spacing.
For now let's assign the most used row spacing of 0.33 m.

>>>>

## Disease pressure factor

@@

median_AUDPC <-
   median(as.vector(Trial_Dpress$AUDPC_C), na.rm = TRUE)
median_AUDPC

@@

## Row spacing

We may want to consider row spacing in the trials.
However one of the locations has `NA` as the row spacing.
For now let's assign the most used row spacing of 0.33 m as an approximation so the model can analyse this as a continuous variable. 
If we decide to use the row_spacing column as a factor in the final model we will need to remove this approximation.
